---
title: "My article"
author: "Bonnie McLean"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    number_sections: yes
    theme: readable
    toc: no
bibliography: references.bib
indent: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(bookdown)

```

# Introduction

Cite articles like this [@johansson_typology_2020], or like this: @johansson_typology_2020 found that blah di blah. Where `@johansson_typology_2020` is the name of the bibtex entry in your file references.bib, where you have all your articles that you are citing in bibtex format.

Cross-referencing is done like this: See section \@ref(materials) for a discussion of the materials. See Figure \@ref(fig:cars-plot) for a plot of some cars.

```{r cars-plot, fig.cap="A plot of some cars."}
plot(cars)
```


See table \@ref(tab:car-table) for some stuff about cars. 

```{r car-table}
knitr::kable(mtcars[1:5, 1:5], caption = "Table about cars")
```


# Method

## Materials {#materials}


## Participants


## Procedure

# Results

# Discussion

# Conclusion

# References
